Revisited hidden weight bit function

### 2024-11-06 RevisedHiddenWeight.tex
a bit of section 6

@@

\subsection{Algebraic immunity of $f$}

@@

 \begin{table}[h!]
	 \centering
	 \begin{tabular}{|c|c|c|c|c|}
		 \hline
		 $n$ & Nonlinearity & Is Balanced & Algebraic Degree & Algebraic Immunity \\
		 \hline
		 2   & 1             & False       & 2               & 1                   \\
		 4   & 4             & True        & 3               & 2                   \\
		 6   & 22            & False       & 5               & 3                   \\
		 8   & 102           & True        & 7               & 4                   \\
		 10  & 458           & False       & 9               & 5                   \\
		 12  & 1902          & True        & 11              & 6                   \\
		 14  & 7842          & False       & 13              & 6                   \\
		 16  & 31680         & True        & 15              & —                   \\
		 \hline
		 \end{tabular}
	 \tablecaption{Characteristics of Boolean Functions for Different $n$ Values}
	 \end{table}

>>>>

\pmnote{under construction, waiting for the parameters for the FAI}

\subsection{Degree}

@@

\begin{table}[h]
	\centering
	\begin{tabular}{|c| c|c|c|c| c|c|c|}
		\hline
		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
		\hline	
		HWBF   & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$  \\  	
		\hline
		Majority   & $4$  & $4$  & $8$  &  $8$ & $8$ & $8$ & $16$  \\
		\hline
		%cyclic $f_0=x_1+x_2x_3$
		t~\cite{DAM:MeaOza24}   & $2$  & $5$  & $6$  &  $9$ & $11$ & $13$ & $14$\\
		\hline	
		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
		u~\cite{DAM:MeaOza24}   & $2$  & $4$  & $6$  &  $8$ & $10$ & $12$ & $14$ \\
		\hline

		$f$  & $3$  & $5$  & $7$  &  $9$ & $11$ & $13$ & $15$\\
		\hline
	\end{tabular}
	\tablecaption{Comparison of the degree.}
	\label{table:comparisonsDeg}
\end{table}

\subsection{Algebraic immunity}

@@

\iffalse
 \begin{table}[h!]
	 \centering
	 \begin{tabular}{|c|c|c|c|c|}
		 \hline
		 $n$ & Nonlinearity & Is Balanced & Algebraic Degree & Algebraic Immunity \\
		 \hline
		 2   & 1             & False       & 2               & 1                   \\
		 4   & 4             & True        & 3               & 2                   \\
		 6   & 22            & False       & 5               & 3                   \\
		 8   & 102           & True        & 7               & 4                   \\
		 10  & 458           & False       & 9               & 5                   \\
		 12  & 1902          & True        & 11              & 6                   \\
		 14  & 7842          & False       & 13              & 6                   \\
		 16  & 31680         & True        & 15              & 7                   \\
		 \hline
		 \end{tabular}
	 \tablecaption{Characteristics of Boolean Functions for Different $n$ Values}
	 \end{table}
\fi

\begin{table}[h]
	\centering
	\begin{tabular}{|c| c|c|c|c| c|c|c|}
		\hline
		$n$ & $4$  & $6$  & $8$  &  $10$ & $12$ & $14$ & $16$  \\
		\hline	
		HWBF   & $2$  & $3$  & $4$  &  $4$ & $5$ & $5$ & $6$  \\  	
		\hline
		Majority   & $2$  & $3$  & $4$  &  $5$ & $6$ & $7$ & $8$  \\
		\hline
		%cyclic $f_0=x_1+x_2x_3$
		t~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $5$ & $6$ & $7$\\
		\hline	
		%$f_0= x_1 + \sum_{i=1}^{n/2-1}x_{2i}x_{2i+1}$	
		u~\cite{DAM:MeaOza24}   & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$ \\
		\hline						
		$f$  & $2$  & $3$  & $4$  &  $5$ & $6$ & $6$ & $7$\\
		\hline
	\end{tabular}
	\tablecaption{Comparison of the algebraic immunity.}
	\label{table:comparisonsAI}
\end{table}

\section{Conclusion and open questions}
\pmnote{TODO or remove}
